Rising from the Ashes II: Did the Birth of the Milky Way's Bar Give Birth to the Birth of the Abundance Bimodality

### 2024-09-10 paper/ms.tex
Add app fig

We examined the abundance distribution in the \MgFe{}-\FeH{} plane of this sample of subhalos by eye. Not many subhalos had multimodal structure, and any structure that was present was relatively weak compared to that observed in the Milky Way. We then applied a post-processing to the \MgFe{} of stars by adding to each star particle a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time of each star particle. With this post-processing, we found that much more structure was generally present. We selected subhalo 172175 (at snapshot 40) for its particular resemblance to the Milky Way. We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99). We refer to this subhalo as our subhalo of interest (SoI).

@@

>>>>

We examined the abundance distribution in the \MgFe{}-\FeH{} plane of this sample of subhalos by eye. Not many subhalos had multimodal structure, and any structure that was present was relatively weak compared to that observed in the Milky Way. We then applied a post-processing to the \MgFe{} of stars by adding to each star particle a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time of each star particle. With this post-processing, we found that much more structure was generally present.

We show the abundance distributions (replicating Figure~\ref{fig:fig1}) of 16 random subhalos from our catalog, and the subhalo we selected, in Appendix~\ref{app:rand_fig1}. Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way. After the $\alpha$-enhancement, a few have strongly bimodal features (subject to interpretation): 172175, 178140, 193025.

We selected subhalo 172175 (the ID at snapshot 40) for its particular resemblance to the Milky Way. We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99). We refer to this subhalo as our subhalo of interest (SoI).

@@

\section{Random Selection of Subhalos}\label{app:rand_fig1}
In Figures~\ref{fig:app0} to \ref{fig:app16}, we show a version of Figure~\ref{fig:fig1} but for a random selection of subhalos from our broader sample of 168 Milky Way-progenitors at $z=1.5$ in TNG50. It is from this sample that we selected our SoI. We first show our SoI at $z=1.5$ in Figure~\ref{fig:app0}, and then show our random sample of 16.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_172175.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for our SoI at $z=1.5$.}
  \label{fig:app0}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_163071.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app1}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_178140.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app2}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_179009.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_193025.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app4}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_196834.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app5}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_202467.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app6}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_208267.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app7}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_222555.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app8}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_235345.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app9}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_245661.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app10}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_254663.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app11}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_260347.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app12}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_265671.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app13}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_282632.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app14}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_287601.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app15}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{fig/app_292983.pdf}
  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
  \label{fig:app16}
\end{figure*}
